Leadership across cultures and contexts: an exploratory analysis

### 2020-06-22 leadership_across_cultures_contexts.Rmd
More edits variation discussion

These four factors were confounded. Specifically, evidence for leadership in residential subgroups and kin groups was relatively more common in hunter-gatherer and pastoralist societies, populations more likely to experience high residential mobility [@wild_making_2019; @rigby_persistent_1985; @kelly_foraging_2013; @venkataraman_hunter-gatherer_2017]. Evidence for supracommunity political leadership was more common in horticultural and agricultural societies, which tend to rely heavily on cultivated land and maintain fixed, defensible territories (Figures \@ref(fig:grouptype) and S\@ref(fig:regionsubsistence)). These patterns support perspectives suggesting residential mobility and increased costs of dispersal, subsistence intensification, and demographic transitions are associated with increasing complexity of sociopolitical organization among nonindustrial populations [@johnson_evolution_1987; @steward_basin-plateau_1938; @powers_evolutionary_2014; @kantner_identifying_2010]. The only example of supracommunity leadership among hunter-gatherers was from the Andamanese by @az02-001[p. 45], who discussed the roles of a "head chief" from a permanent residential location and their marginal influence over other, local residential leaders (see quote in *Coding example* section of SI). One interpretation of the negative relationship between evidence for political leadership at the community level or above and leadership in kin groups or residential groups is that as political structures become more institutionalized and economic systems transcend the household, leadership within households and residential groups diminishes.

>>>>

These four factors were confounded. Evidence for leadership in residential subgroups and kin groups was relatively more common in hunter-gatherer and pastoralist societies, populations more likely to experience high residential mobility [@wild_making_2019; @rigby_persistent_1985; @kelly_foraging_2013; @venkataraman_hunter-gatherer_2017]. Evidence for supracommunity political leadership was more common in horticultural and agricultural societies, which tend to rely heavily on cultivated land and maintain fixed, defensible territories (Figures \@ref(fig:grouptype) and S\@ref(fig:regionsubsistence)). These patterns support perspectives suggesting residential mobility and subsistence intensification are associated with increasing complexity of sociopolitical organization [@johnson_evolution_1987; @steward_basin-plateau_1938; @powers_evolutionary_2014; @kantner_identifying_2010]. The only example of supracommunity leadership among hunter-gatherers was from the Andamanese by @az02-001[p. 45], who discussed the roles of a "head chief" from a permanent residential location and their marginal influence over other, local residential leaders (see quote in *Coding example* section of SI). One interpretation of this trend is that as political structures become more institutionalized and economic systems transcend the household, leadership within households and residential groups diminishes.
